XRONOS: an open data infrastructure for archaeological chronology

### 2024-12-05 paper.qmd
Fix table width

```{r tbl-issues}
#| tbl-cap: Automatically-recognised data quality issues currently implemented in XRONOS
tribble(
  ~entity,                    ~issue_code,            ~n,     ~issue_description,
  "Sites",                    "MISSING_COORDINATES",  4452,   "Missing geographic coordinates",
  "Sites",                    "INVALID_COORDINATES",  0,      "Geographic coordinates fall outside the earth's ellipsoid",
  "Sites",                    "MISSING_COUNTRY_CODE", 1221,   "Missing data on what country the site is in",
  "Samples",                  "MISSING_MATERIAL",     138177, "Missing data on the sample material",
  "Samples",                  "MISSING_TAXON",        138182, "Missing data on the sample taxon",
  "Samples",                  "MISSING_CRS",          0,      "Sample has coordinates but the coordinate reference system is not given",
  "Taxons",                   "UNKNOWN_TAXON",        9260,   "Sample taxon has not been matched to the GBIF Backbone Taxonomy",
  "Taxons",                   "LONG_TAXON",           509,    "Description of the sample taxon is implausibly long",
  "Radiocarbon dates",        "MISSING_C14_AGE",      447,    "Missing radiocarbon age",
  "Radiocarbon dates",        "VERY_OLD_C14",         76,     "Radiocarbon age older than the effective range of the method (50 ka)",
  "Radiocarbon dates",        "MISSING_C14_ERROR",    585,    "Missing measurement error",
  "Radiocarbon dates",        "MISSING_D14C",         238875, "Missing δ13C measurement",
  "Radiocarbon dates",        "MISSING_D14C_ERROR",   238875, "Missing δ13C measurement error",
  "Radiocarbon dates",        "MISSING_C14_METHOD",   242233, "Missing data on radiocarbon dating method (conventional, AMS, etc.)",
  "Radiocarbon dates",        "MISSING_C14_LAB_ID",   1233,   "Missing laboratory identifier",
  "Radiocarbon dates",        "INVALID_LAB_ID",       16053,  "Laboratory identifier does not match the standard format (e.g. 'Abc-1234')",
  "Radiocarbon dates",        "MISSING_C14_LAB",      350190, "Missing data on the radiocarbon laboratory",
  "Bibliographic references", "MIXED_REFERENCE",      21933,  "Bibliographic reference appears to combine multiple publications",
  "Bibliographic references", "MISSING_BIBTEX",       42109,  "Bibliographic reference without structured data in BibTeX format",
) |>
  group_by(entity) |>
  gt() |>
  cols_label(issue_code = "Issue", n = "N", issue_description = "Description") |>
  cols_width(everything() ~ pct(33)) |> # TODO: fix...
  tab_options(
    table.font.size = 13
  )
```

>>>>

```{r tbl-issues}
#| tbl-cap: Automatically-recognised data quality issues currently implemented in XRONOS
tribble(
  ~entity,                    ~issue_code,            ~n,     ~issue_description,
  "Sites",                    "MISSING_COORDINATES",  4452,   "Missing geographic coordinates",
  "Sites",                    "INVALID_COORDINATES",  0,      "Geographic coordinates fall outside the earth's ellipsoid",
  "Sites",                    "MISSING_COUNTRY_CODE", 1221,   "Missing data on what country the site is in",
  "Samples",                  "MISSING_MATERIAL",     138177, "Missing data on the sample material",
  "Samples",                  "MISSING_TAXON",        138182, "Missing data on the sample taxon",
  "Samples",                  "MISSING_CRS",          0,      "Sample has coordinates but the coordinate reference system is not given",
  "Taxons",                   "UNKNOWN_TAXON",        9260,   "Sample taxon has not been matched to the GBIF Backbone Taxonomy",
  "Taxons",                   "LONG_TAXON",           509,    "Description of the sample taxon is implausibly long",
  "Radiocarbon dates",        "MISSING_C14_AGE",      447,    "Missing radiocarbon age",
  "Radiocarbon dates",        "VERY_OLD_C14",         76,     "Radiocarbon age older than the effective range of the method (50 ka)",
  "Radiocarbon dates",        "MISSING_C14_ERROR",    585,    "Missing measurement error",
  "Radiocarbon dates",        "MISSING_D14C",         238875, "Missing δ13C measurement",
  "Radiocarbon dates",        "MISSING_D14C_ERROR",   238875, "Missing δ13C measurement error",
  "Radiocarbon dates",        "MISSING_C14_METHOD",   242233, "Missing data on radiocarbon dating method (conventional, AMS, etc.)",
  "Radiocarbon dates",        "MISSING_C14_LAB_ID",   1233,   "Missing laboratory identifier",
  "Radiocarbon dates",        "INVALID_LAB_ID",       16053,  "Laboratory identifier does not match the standard format (e.g. 'Abc-1234')",
  "Radiocarbon dates",        "MISSING_C14_LAB",      350190, "Missing data on the radiocarbon laboratory",
  "Bibliographic references", "MIXED_REFERENCE",      21933,  "Bibliographic reference appears to combine multiple publications",
  "Bibliographic references", "MISSING_BIBTEX",       42109,  "Bibliographic reference without structured data in BibTeX format",
) |>
  group_by(entity) |>
  gt() |>
  cols_label(issue_code = "Issue", n = "N", issue_description = "Description") |>
  cols_width(
    issue_code ~ pct(30),
    n ~ pct(20),
    issue_description ~ pct(50)
  ) |>
  tab_options(
    table.font.size = 13
  )
```
